---
title: "DSS"
author: "Yuhang Zhu"
date: "2023-09-06"
output: github_document
---
# Introduction

```{r install, eval = FALSE}
library(tidyverse)
library(socviz)
```

```{r setup, , include = FALSE}
setwd("~/Desktop/UC Merced/PhD/2.First Year/POLI210/DSS")
```


# 2.Estimating Casual Effects with Randomized Experiments

## 2.1 Project Start

## 2.2 Treatment and Outcome Variables

*X* -> *Y*

### 2.2.1 Treatment Variables

X~i~ = 1 (treatment) or = 0 (control)

### 2.2.2 Outcome Varibales
reading, math, and graduated

## 2.3 Individual Causal Effects

causal effect of *X* on *Y*

a change in the outcome as $\Delta$*Y*

*Y*~i~(*X*~i~=1) -> potential outcome under the treatment condition for individual *i*

*Y*~i~(*X*~i~=0) -> potential outcome under the control condition for individual *i*

*individual_effects*~i~ = $\Delta$*Y*~i~ = *Y*~i~(*X*~i~=1) - *Y*~i~(*X*~i~=0)

We can never observe the **counter-factual outcome**, which is the potential outcome that would have occurred under whichever condition was not received in reality.

**The fundamental problem we face when inferring causal effects is that we never observe the same individual both receiving the treatment and not receiving the treatment at the same time.**

## 2.4 Average Causal Effects

**Average causal effect** of the treatment *X* on the outcome *Y*, also known as the **average treatment effect**, is the average of all the individual causal effects ox *X* on *Y* within a group.

$\overline{\mathit{individual\_effects}}$ = $\frac{\sum_{i = 1}^{n} \mathit{individual\_effects}}{\ n}$

We must find or create a situation in which the treated observations and the untreated observations are similar with respect to all the variables that might affect the outcome other than the treatment variable itself. The best way to accomplish this is by conducting a randomized experiment.

### 2.4.1 Randomized Experiments and the Difference-in-means Estimator

**Randomized experiment** / **randomized controlled trial (RCT)** to make two groups are comparable to each other, *on average*, in all respects other than whether or not they received the treatment.

**Pre-treatment characteristics** are the characteristics of the individuals in a study before the treatment is administered.

average_effect = ${\overline{Y(X=1) - Y(=0)}}$ = ${\overline{Y(X=1)}}$ - ${\overline{Y(X=0)}}$

```{r}

```

