---
title: "HW_B1"
author: "Yuhang Zhu"
date: "2023-09-17"
output: github_document
---

```{r setup, include = FALSE}
getwd()

library(tidyverse)
```

# Indiscriminate Violence and Insurgency

```{r input_violenc, include = FALSE}
jcr <- read.csv("B1/chechen.csv")
```

```{r view_violence, include = FALSE}
dim(jcr)

head(jcr)
```

## Question 1

According to the variable `fire`, there are 159 villages were attacked by Russians and 159 were not attacked.

```{r q1_violence}
table(jcr$fire)
```

## Question 2

Yes.  

The estimated number of individuals killed during Russian artillery fire in Groznyy villages is on average `r 3.71-1.57` more than in villages outside Groznyy.

According to the median, the number in Grozny villages is `r 3-0` higher than in villages outside Grozny.

```{r q2_violence}
deaths_groznyy <- jcr %>%
  group_by(groznyy) %>%
  summarise(mean_deaths = mean(deaths, na.rm = TRUE),
            median_deaths = median(deaths, na.rm = TRUE)) %>% 
  round(2)

deaths_groznyy
```

## Question 3

For villages hit by artillery fire, the average number of insurgent attacks was fewer than for those not hit. The difference is -0.55. However, the `postattack` distributions for villages that were hit and those that were not are similar. 

We cannot definitively conclude that indiscriminate violence reduces insurgent attacks, as the Russians may not attack villages randomly. According to evidence from **Question 2**, villages in Groznyy are more susceptible to attacks. If the dataset doesn't come from a randomized experiment, the treatment (`fire == 1`) and control (`fire == 0`) groups may not be comparable based on their pre-treatment characteristics.

```{r q3_violence}
sum_postattack <- jcr %>%
  group_by(fire) %>%
  summarise(m_postattack = mean(postattack, na.rm = TRUE),
            qtl_0_postattack = quantile(postattack, probs = 0, na.rm = T),
            qtl_25_postattack = quantile(postattack, probs = 0.25, na.rm = T),
            qtl_50_postattack = quantile(postattack, probs = 0.5, na.rm = T),
            qtl_75_postattack = quantile(postattack, probs = 0.75, na.rm = T),
            qtl_100_postattack = quantile(postattack, probs = 1, na.rm = T))

sum_postattack

diff_postattack <- sum_postattack$m_postattack[sum_postattack$fire == 1] - sum_postattack$m_postattack[sum_postattack$fire == 0]

diff_postattack
```

## Question 4

The difference in the average number is `r round(mean(jcr$preattack[jcr$fire == 1]) - mean(jcr$preattack[jcr$fire == 0]), 2)`, indicating that villages had similar numbers of insurgent attacks prior to Russian artillery fire. Given the similarity in the key variable `the number of insurgent attacks` prior to the treatment (`fire`), the validity of the previously used identification strategy is partially confirmed.

```{r q4_violence}
diff_preattack <- mean(jcr$preattack[jcr$fire == 1]) - mean(jcr$preattack[jcr$fire == 0])

diff_preattack
```

## Question 5

The number of insurgent attacks actually decreased, rather than increased, following the artillery fire. Among the villages shelled by Russians, the average number of insurgent attacks decreased by -0.62 after the fire.

```{r q5_violence}
jcr$diffattack <- jcr$postattack - jcr$preattack

diff_attack_fire <- mean(jcr$diffattack[jcr$fire == 1])

diff_attack_fire
```


## Question 6

This identification strategy **supports** the claim that indiscriminate violence reduces insurgency attacks, and its validity is improved relative to prior strategies. By using the strategy (\( T_{2} \) - \( T_{1} \)) - (\( C_{2} \) - \( C_{1} \)), this paper isolates the net treatment effect of `indiscriminate violenc` on the `number of insurgency attacks` (-0.516). \( T_{2} \) - \( T_{1} \) determines the treatment effect (`indiscriminate violenc`) on the `number of insurgency attacks` (-0.616), whereas \( C_{2} \) - \( C_{1} \) represents the original trend without treatment effect (-0.101).

| Variables     | Pre-attack                       | post-attack                    |                                 |
|:--------------|:---------------------------------|:-------------------------------|:--------------------------------|
| `fire == 1`   |  \( T_{1} \)                     | \( T_{2} \)                    | \( T_{2} \) - \( T_{1} \) (Q5)  |            
| `fire == 0`   |  \( C_{1} \)                     | \( C_{2} \)                    | \( C_{2} \) - \( C_{1} \) (Q6)  |            
|               |  \( T_{1} \) - \( C_{1} \) (Q4)  | \( T_{2} \) - \( C_{2} \) (Q3) | \( \beta_{DD} \) (Q6)           |            

```{r q6_violence}
m_diffattack <- mean(jcr$diffattack[jcr$fire == 1]) - mean(jcr$diffattack[jcr$fire == 0])

m_diffattack
```

```{r did_violence}
# double check
did <-  (mean(jcr$postattack[jcr$fire == 1]) - mean(jcr$preattack[jcr$fire == 1])) - 
  (mean(jcr$postattack[jcr$fire == 0]) - mean(jcr$preattack[jcr$fire == 0]))

did
```

# Inequality of Success in Online Music Markets

```{r input_music, include = FALSE}
songs1 <- read.csv("B1/music-data/songs1.csv")

songs2 <- read.csv("B1/music-data/songs2.csv")

users1 <- read.csv("B1/music-data/users1.csv")

users2 <- read.csv("B1/music-data/users2.csv")
```

```{r view_music, include = FALSE }
head(songs1)
dim(songs1)

head(songs2)
dim(songs2)

head(users1)
dim(users1)

head(users2)
dim(users2)
```

## Question 1

In **Experiment 1**, the proportions of users assigned for the *Social Influence* and *Independent* condition are 33% and 67%, respectively.

In **Experiment 2**, the proportions of users assigned for the *Social Influence* and *Independent* condition are 32% and 68%, respectively.

```{r q1_music}
# exp1
p_exp1 <- prop.table(table(users1$world_id))

print(round(p_exp1, 2))

# exp1
p_exp2 <- prop.table(table(users2$world_id))

print(round(p_exp2, 2))
```
## Question 2

In **Experiment 1**, the average number of downloads per user in the treatment group (*Social Influence*) is `r 1.1-0.94` lower than control group (*Independent*), while the average number of listens per user is `3.51-1.71` higher. These results suggest that users under *Social influence* have a lower average number of downloads compared to those in the *Independent* group. Conversely, the average number of songs listened to is higher than that for users in the *Independent* group. In **Experiment 2**, the results remain.

```{r q2_music}

table(users1$world_id)

table(users2$world_id)

# exp1: average number of downloads per user

m_exp1_down_soc <- sum(songs1$down_soc) / 702

print(round(m_exp1_down_soc, 2))

m_exp1_down_indep <- sum(songs1$down_indep) / 1441

print(round(m_exp1_down_indep, 2))

# exp2:average number of downloads per user

m_exp2_down_soc <- sum(songs1$down_soc) / 689

print(round(m_exp2_down_soc, 2))

m_exp2_down_indep <- sum(songs2$down_indep) / 1446

print(round(m_exp2_down_indep, 2))

# exp1: average number of listening per user

m_exp1_lis_soc <- sum(songs1$listen_soc) / 702

print(round(m_exp1_lis_soc, 2))

m_exp1_lis_indep <- sum(songs1$listen_soc) / 1441

print(round(m_exp1_lis_indep, 2))

# exp2: average number of listening per user

m_exp2_lis_soc <- sum(songs2$listen_soc) / 689

print(round(m_exp2_lis_soc, 2))

m_exp2_lis_indep <- sum(songs2$listen_soc) / 1446

print(round(m_exp2_lis_indep, 2))
```


## Question 3

```{r q3_music_package, include = FALSE}
# install.packages("ineq")

library(ineq)

# help(ineq)
```

In both **Experiment 1** and **Experiment 2**, the Gini coefficient for *Social Influence* (0.33 and 0.46, respectively) is higher than that for *Independent* (0.24 and 0.19 respectively). This suggests that in the treatment group, some songs are downloaded more frequently than others, whereas downloads are more evenly distributed among songs in the control group. Thus, the hypothesis that social influence increases the inequality of success in the music market is supported. The same conclusion holds when analyzing the number of times each song was listened to.

```{r q3_music}
# exp1 download
ineq_exp1_soc_down <- Gini(songs1$down_soc)

print(round(ineq_exp1_soc_down, 2))

ineq_exp1_indep_down <- Gini(songs1$down_indep)

print(round(ineq_exp1_indep_down, 2))

# exp2 download
ineq_exp2_soc_down <- Gini(songs2$down_soc)

print(round(ineq_exp2_soc_down, 2))

ineq_exp2_indep_down <- Gini(songs2$down_indep)

print(round(ineq_exp2_indep_down, 2))

# exp1 listen
ineq_exp1_soc_lis <- Gini(songs1$listen_soc)

print(round(ineq_exp1_soc_lis, 2))

ineq_exp1_indep_lis <- Gini(songs1$listen_indep)

print(round(ineq_exp1_indep_lis, 2))

# exp2 listen
ineq_exp2_soc_lis <- Gini(songs2$listen_soc)

print(round(ineq_exp2_soc_lis, 2))

ineq_exp2_indep_lis <- Gini(songs2$listen_indep)

print(round(ineq_exp2_indep_lis, 2))
```

## Question 4

According to the table, the pre-treatment characteristics are balanced between treatment group and control group, validating the randomized **Experiment 1** and **Experiment 2**. Based on the randomized experiments, the conclusions draw from the previous question are credible.

```{r q4_music}
# exp1
user1_charct <- users1 %>% 
  group_by(world_id) %>% 
  summarise(mean_web = mean(web, na.rm = TRUE),
            mean_visit = mean(visit, na.rm = TRUE),
            mean_purchase = mean(web, na.rm = TRUE),) %>% 
  round(2)

user1_charct

# exp2
user2_charct <- users2 %>% 
  group_by(world_id) %>% 
  summarise(mean_web = mean(web, na.rm = TRUE),
            mean_visit = mean(visit, na.rm = TRUE),
            mean_purchase = mean(web, na.rm = TRUE),) %>% 
  round(2)

user2_charct
```


## Question 5

The difference implies that if the songs were ordered according to the number of downloads, the inequality of success will expand. However, due to the experimental design, this between-study comparison doesn't have as much internal validity as the within-study comparison. The two experiments were conducted sequentially, meaning that no randomization was employed in assigning users to either of the two experiments. Lacking of the randomization, users in the *Experiment 1* and in the * Experiment 2* could be systematically different, thereby reducing the internal validity when comparing the estimated average effect between them. For example, the average number of `visit` among users in the treatment group is higher in *Experiment 2* (1.96) than in *Experiment 1* (1.87). Thus, `visit` is a potential confounder.
 
```{r q5_musci}
# downloads
diff_exp_down <- (ineq_exp1_soc_down - ineq_exp1_indep_down) - (ineq_exp2_soc_down - ineq_exp2_indep_down)

diff_exp_down

# listens
diff_exp_lis <- (ineq_exp1_soc_lis - ineq_exp1_indep_lis) - (ineq_exp2_soc_lis - ineq_exp2_indep_lis)

diff_exp_lis
```

