---
title: "HW_B2"
author: "Yuhang Zhu"
date: "2023-10-02"
output: github_document
---

```{r setup, include = FALSE}
getwd()

library(tidyverse)
```

# Predicting Course Grades Using Midterm Scores Part I: Predicting Final Exam Scores

```{r import_grades}
grades <- read.csv("B2/grades.csv")

head(grades)

dim(grades)
```

## 1. First, let’s ﬁgure out what each observation represents, identify our X and Y variables, and explore whether they are moderately or strongly linearly associated with each other.

### 1a

Each observation represents a student's midterm score, final score, overall score, and whether they earned an A or A-.

### 1b

Our independent variable, `midterm`, is numeric and not binary.

```{r part1_q1b}
str(grades)

summary(grades$midterm)
```

### 1c

Our dependent variable, `final`, is also numeric and not binary.

```{r part1_q1c}
summary(grades$final)
```

### 1d

The correlation coeﬃcient between X and Y is strongly linear.

```{r part1_q1d}
cor(grades$midterm, grades$final)
```

## 2. Second, let’s ﬁt the linear model that we will use to make predictions.

### 2a

```{r part1_q2a}
fit <- lm(final ~ midterm, grades)

fit
```
### 2b

$$\hat{final} = -6.0059 + 0.9704 midterm $$ 

### 2c

```{r part1_q2c}
plot(grades$midterm, grades$final,
     xlab = "Midterm Scores",
     ylab = "Final Scores",
     main = "Midterm Scores and Final Scores")
abline(lm(final ~ midterm, grades), lty = "dashed")

# also:
ggplot(grades, aes(midterm, final)) +
  geom_point() +
  geom_smooth(method = lm, se = F) +
  labs(x = "Midterm Scores", 
       y = "Final Scores",
       title = "Midterm Scores and Final Scores")
```

## 3. Now, let’s use the ﬁtted line to make some predictions.

### 3a

If a student earns 80 points in the midterm, the points he or she may earn in the final exam are 71.6.

```{r part1_q3a}
-6.0059 + 0.9704 * 80
```

### 3b

If a student earns 90 points in the midterm, the points he or she may earn in the final exam are 81.3.

```{r part1_q3b}
-6.0059 + 0.9704 * 90
```

### 3c

If a student earns extra 10 points in the midterm, the extra points he or she may earn in the final exam are 9.7.

```{r part1_q3c}
0.9704 * 10
```

## 4. What is the R^2^ of the ﬁtted model? And, how would you interpret it?

The R^2^ of the fitted model is 0.51, which indicates that 51% variance in final exam scores can be explained by midterm scores.

```{r part1_q4}
r <- cor(grades$midterm, grades$final)
r2 <- r * r
r2

# also:
fit_model <- summary(fit)
r_square <- fit_model$r.squared
r_square
```

# Evidence of Data Fabrication

```{r import_gay_ccap}
gay <- read.csv("B2/gay.csv")
ccap <- read.csv("B2/CCAP.csv")

head(gay, 4)
head(ccap, 4)

dim(gay)
dim(ccap)
```

## Question 1

Yes, these two distributions look similar. 

```{r part2_q1}
ggplot(ccap, aes(feel, after_stat(density))) +
  geom_histogram(binwidth=10) +
  labs(x = "Feeling towards gay men and lesbian women",
       y = "Density")

ggplot(gay, aes(feel1, after_stat(density))) +
  geom_histogram(binwidth=10) +
  labs(x = "Feeling towards gay men and lesbian women",
       y = "Density")
```

## Question 2

Yes, the two distributions have similar descriptive statistics.

```{r part2_q2}
sum_ccap <- ccap %>% 
  summarise(mean_feel = mean(feel, na.rm = TRUE),
            median_feel = median(feel, na.rm = TRUE),
            sd_feel = sd(feel, na.rm = TRUE))
sum_ccap

sum_gay <- gay %>% 
  summarise(mean_feel1 = mean(feel1, na.rm = TRUE),
            median_feel1 = median(feel1, na.rm = TRUE),
            sd_feel1 = sd(feel1, na.rm = TRUE))
sum_gay
```

## Question 3

The demographic characteristics of the national sample differ from those of Los Angeles County. Thus, the similarity between the two distributions is unexpected.

## Question 4

Yes. The respondents in the gay marriage experiment dataset have relatively stable feelings over the whole period of time.

```{r part2_q4, warning=FALSE}
control <- c("No Contact")

# 4a
ggplot(subset(gay, subset = treatment %in% control),
       aes(feel1, feel2)) +
  geom_point()

# 4b
ggplot(subset(gay, subset = treatment %in% control),
       aes(feel1, feel3)) +
  geom_point()

# 4c
ggplot(subset(gay, subset = treatment %in% control),
       aes(feel1, feel4)) +
  geom_point()
```

## Question 5

Yes. These variables highly correlated with each other.

```{r part2_q5}
# 5a
cor(gay$feel1[gay$treatment=="No Contact"], gay$feel2[gay$treatment=="No Contact"], use = "complete.obs")

# 5b
cor(gay$feel1[gay$treatment=="No Contact"], gay$feel3[gay$treatment=="No Contact"], use = "complete.obs")

# 5c
cor(gay$feel1[gay$treatment=="No Contact"], gay$feel4[gay$treatment=="No Contact"], use = "complete.obs")
```

## Question 6

Yes.


