---
title: "Homework B5"
output: html_notebook
---

Your assignment is to replicate, as best you can, each panel of Figure 1 (A, B, and, C) from the article:

LeVeck, B. L., Hughes, D. A., Fowler, J. H., Hafner-Burton, E. & Victor, D. G. The role of self-interest in elite bargaining. Proceedings of the National Academy of Sciences of the United States of America 111, 18536–18541 (2014).

For each panel (A, B, and C), make a graph that is as close as possible to the graph shown in the paper.

After each graph, display the dataset used by the graph.

You can find a copy of the article at:
http://faculty.ucmerced.edu/bleveck/assets/pdfs/role_of_self_interest_in_elite_bargaining.pdf

You can find a copy of the datasets at:
https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/27894

The core part of this assignment will be to calculate the standard errors, which are plotted as whiskers on top of the bar graphs (whiskers are 1 standard error of the mean in each direction). You can calculate the standard errors under the assumption that both elite and non-elite subject pools are random samples from their respective populations. To do this create a function called `sem`, which takes a variable and calculates the standard error of the mean, under the assumption that each observation is randomly, independently sampled from a broader population. I've started the code for you below.

Note, some of the standard errors in the actual paper are calculated using an estimation technique called the non-parametic bootstrap. We'll discuss this in a future class, but for now just know that your estimates may differ from the paper's by a little bit. 

```{r}
# takes a numeric vector and returns a standard error of the mean
sem <- function(x){
  if(!is.numeric(x)){
    "Error: x needs to be a numeric variable"
  }
  x_complete <- na.omit(x)
  n <- length() # fill this in
  sd_hat <- # estimate standard deviation of the variable using the sd() function, or code your own.
  sem <- # calcuate sem
  return(sem)    
}
```

Next, create a test statistic as described in lecture and the notes. Test the null hypothesis that that the difference between elite and undergraduate MA0's is 0. Use an alpha 0.05. 

```{r}
D_hat <- ## insert difference in means estimator
se_D_hat <- ##  calculate standard error for difference in means estimator using notes / slides
test_statistic <- (D_hat - 0)/se_D_hat

pnorm() # use pnorm to analyze the test statistic under the null hypothesis as shown in the lecture slides
```
  