---
title: "HW_B3"
author: "Yuhang Zhu"
date: "2023-10-13"
output: github_document
---

## Chapter 1 problems (1.9 exercises)

### Problem 22

#### Solution

```{r, include = FALSE}
(factorial(3) * factorial(3))/factorial(6)
```

$\frac{3! \times 3!}{6!} = \frac{1}{20} \ or \  0.05$

#### Simulation

```{r q22}
sims <- 100000

sex <- c("boy", "boy", "boy", "girl", "girl", "girl")

count <- 0

for(i in 1:sims) {
  ## random order
  order <- sample(sex)
  ## from 1st to 3rd are girls
  if(order[1] == "girl" & order[2] == "girl" & order[3] == "girl") {
    count <- count + 1}
}

prob <- count / sims

print(round(prob, 2))
```

### Problem 34

#### Solution

```{r, include = FALSE}
(choose(30, 5) * choose(25, 5) * choose(20, 5) * choose(15, 5) * choose(10, 5) * choose(5, 5)) / 6^30
```

$\frac{C(30, 5) \times C(25, 5) \times C(20, 5) \times C(15, 5) \times C(10, 5) \times C(5, 5)}{6^{30}} \approx 0.0004$

#### Simulation

```{r q34}
sims <- 1000000

count <- 0

for(i in 1:sims) {
  outcome <- sample(1:6, 30, replace = T)
  if(sum(outcome == 1) == 5 & 
     sum(outcome == 2) == 5 & 
     sum(outcome == 3) == 5 & 
     sum(outcome == 4) == 5 & 
     sum(outcome == 5) == 5 & 
     sum(outcome == 6) == 5) {
    count <- count + 1
  }
}

prob <- count / sims

prob
```

## Chapter 2 problems (2.11 exercises)

### Problem 2

#### Solution

```{r, include = FALSE}
((1/2) * (1/3)) / (((1/2) * (1/3)) + ((1/2) * (1/2) * (1 - 1/3)))
```

$$
P(identical | boys) = 
  \frac{P(identical \cap boys)}{P(boys)} = 
  \frac{P(boys | identical)P(identical)}{P(boys | identical)P(identical) + P(boys | fraternal)P(fraternal)} =
  \frac{1}{2}
$$

#### Simulation

```{r q2}
sims <- 100000

says_boys <- says_identical_boys <- rep(NA, sims)

for(i in 1:sims) {
   is_identical <- sample(c("identical", "fraternal"), size = 1, prob = c(1/3, 2/3))
   
   if(is_identical == "identical") {
     says <- sample(c("boys", "not_boys"), size = 1, prob = c(1/2, 1/2))
   }
   else{
     says <- sample(c("boys", "not_boys"), size = 1, prob = c(1/4, 3/4))
   }
   
   ifelse(says == "boys", says_boys[i] <- 1, says_boys[i] <- 0)
   ifelse(says == "boys" && is_identical == "identical", says_identical_boys[i] <- 1, says_identical_boys[i] <- 0)
}

invisible(mean(says_boys))
invisible(mean(says_identical_boys))

print(round(mean(says_identical_boys) / mean(says_boys), 2))
```

### Problem 32

#### (a)

##### Solution

$P(A > B)$ = $\frac{4}{6}$ = $\frac{2}{3}$

$P(B > C)$ = $\frac{4}{6}$ = $\frac{2}{3}$

$P(C > D)$ = $P(C = 6) + P(C=2 \cap D=1)$ = $\frac{2}{3}$ = `r round(2/6 + 4/6 * 1/2, 2)`

$P(D > A)$ = $P(D = 5) + P(D=1 \cap A=0)$ = $\frac{2}{3}$ = `r round(3/6 + 3/6 * 2/6, 2)`

##### Simulation

```{r q32a}
sims <- 100000

dice_a <- c(4, 4, 4, 4, 0, 0)
dice_b <- c(3, 3, 3, 3, 3, 3)
dice_c <- c(6, 6, 2, 2, 2, 2)
dice_d <- c(5, 5, 5, 1, 1, 1)

count_ab <- 0
count_bc <- 0
count_cd <- 0
count_da <- 0

for (i in 1:sims) {
  outcome_a <- sample(dice_a, size = 1, replace = T)
  outcome_b <- sample(dice_b, size = 1, replace = T)
  outcome_c <- sample(dice_c, size = 1, replace = T)
  outcome_d <- sample(dice_d, size = 1, replace = T)
  
  if(outcome_a > outcome_b) {
    count_ab <- count_ab + 1
  }
  
  if(outcome_b > outcome_c) {
    count_bc <- count_bc + 1
  }
  
  if(outcome_c > outcome_d) {
    count_cd <- count_cd + 1
  }
  
  if(outcome_d > outcome_a) {
    count_da <- count_da + 1
  }
}

prbs_ab <- count_ab / sims
print(round(prbs_ab, 2))

prbs_bc <- count_bc / sims
print(round(prbs_bc, 2))

prbs_cd <- count_cd / sims
print(round(prbs_cd, 2))

prbs_da <- count_da / sims
print(round(prbs_da, 2))
```

#### (b)

##### Solution

$\because P(A>B>C) = \frac{4}{6} \times \frac{4}{6} = P(A > B) \times P(B > C) = \frac{4}{6} \times \frac{4}{6}$

$\therefore A > B \text{ is independent of the event } B > C$

$\because P(B>C>D) = \frac{4}{6} \times \frac{3}{6} \ne P(B > C) \times P(C > D) = \frac{4}{6} \times \frac{4}{6}$

$\therefore B > C \text{ is not independent of the event } C > D$

##### Simulation

```{r q32b}
sims <- 100000

dice_a <- c(4, 4, 4, 4, 0, 0)
dice_b <- c(3, 3, 3, 3, 3, 3)
dice_c <- c(6, 6, 2, 2, 2, 2)
dice_d <- c(5, 5, 5, 1, 1, 1)

count_abc <- 0
count_bcd <- 0

for (i in 1:sims) {
  outcome_a <- sample(dice_a, size = 1, replace = T)
  outcome_b <- sample(dice_b, size = 1, replace = T)
  outcome_c <- sample(dice_c, size = 1, replace = T)
  outcome_d <- sample(dice_d, size = 1, replace = T)

  if(outcome_a > outcome_b & outcome_b > outcome_c) {
    count_abc <- count_abc + 1
  }
  
  if(outcome_b > outcome_c & outcome_c > outcome_d) {
    count_bcd <- count_bcd + 1
  }
}

prbs_abc <- count_abc / sims
print(round(prbs_abc, 2))

prbs_bcd <- count_bcd / sims
print(round(prbs_bcd, 2))
```

### Problem 38 part (a)

#### Solution

Without loss of generality, we can assume the contestant picked door 1. Let $C_i$ be the event that the car is behind door $i$, for $i = 1, 2, 3, 4, 5, 6, 7$. By the law of total probability,

$$
P(get \ car) = P(get \ car | C_1) \times \frac{1}{7} + P(get \ car | C_2) \times \frac{1}{7} + \ldots + P(get \ car | C_7) \times \frac{1}{7}
$$

Suppose the contestant employs the switching strategy.

-   If the car is behind door 1, then switching will fail, so $P(get \ car | C_1) = 0$.

-   If the car is behind door 2 to 7, then because Monty always reveals a goat, the remaining 3 unopened door contain the car, so the probability of winning by switching is $\frac{1}{3}$. Thus,

$$
P(get \ car) = 0 \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} + \frac{1}{3} \times \frac{1}{7} =  \frac{2}{7}
$$

Suppose the contestant employs the non-switching strategy.

-   If the car is behind door 1, then non-switching will success, so $P(get \ car | C_1) = \frac{1}{7}$.

-   If the car is behind door 2 to 7, then non-switching will always lose.

Thus, you should employs the switching strategy.

#### Simulation

```{r q38a}
sims <- 100000
doors <- c("goat", "goat", "goat", "goat", "goat", "goat", "car")
result.switch <- result.noswitch <- rep(NA, sims)

for (i in 1:sims) {
  first <- sample(1:7, size = 1)
  
  result.noswitch[i] <- doors[first]
  
  remain <- doors[-first]

  if (doors[first] == "car") 
    monty <- sample(1:6, size=3)
  else
    monty <- sample((1:6)[remain == "goat"], 3)
  
  result.switch[i] <- sample(remain[-monty], 1)
}

mean(result.noswitch == "car")
mean(result.switch == "car")
```

### Problem 38 part (b)

#### Solution

Abstracting from 38(a):

Without loss of generality, we can assume the contestant picked door 1. Let $C_i$ be the event that the car is behind door $i$, for $i = 1, 2, 3, \ldots, n$. By the law of total probability,

$$
P(get \ car) = \sum_{i=1}^nP(get \ car | C_n)
$$

Suppose the contestant employs the non-switching strategy.

-   If the car is behind door 1, then non-switching will success, so $P(get \ car | C_1) = \frac{1}{n}$.

-   If the car is behind door 2 to $n$, then non-switching will always lose. And the probability is $\frac{n-1}{n}$

Suppose the contestant employs the switching strategy.

-   If the car is behind door 1, then switching will fail, so $P(get \ car | C_1) = 0$. And the probability is $\frac{1}{n}$.

-   If the car is behind door 2 to $n$, then because Monty always reveals a goat, the remaining $n-1-m$ unopened door contain the car, so the probability of winning by switching is $\frac{1}{n-m-1}$. Thus,

$$
P(get \ car) = 0 \times \frac{1}{n} + \frac{1}{n-m-1} \times \frac{1}{n} \times (n-1) = \frac{n-1}{n(n-m-1)}
$$

#### Simulation

```{r q28b}
## Declaration: use ChatGPT to learn new functions, explain codes, and debug.
## One confusing part is generating the number of cars and goats. From what I understand the question, I think we should create n doors, 1 car, and n-1 goats;  since m is the number of doors with goats that Monty opens, not the number of all actual doors with goats.
## The most difficult part for me is the subsetting (removing the first and Monty from the doors), because one is a number sequence(1:n), and another is a character sequence("goat", "car"). By using setdiff(), I finally solved this problem.

part_b_sim <- function(m, n){
  # Error messages if m and n are invalid numbers
  if(n < 3){
    return("error: n must be the number of doors >= 3")
  }
  if(m > n - 2 | m < 1){
    return("error: m must be a number of goats that is >= 1 and <= n-2")
  }
  
  # setting up values to store simulations
  sims <- 1e5 # 100000 sims
  result.switch <- result.noswitch <- rep(NA, sims) # vectors for storing sim results
  
  # create doors as in the original example, but with m goats and n-m cars,
  # rather than 2 goats and 1 car.
  doors <- c(rep("goat", n-1), "car") # I recreate the doors.
  
  # for loop for simulations
  for(i in 1:sims) {
    ## YOUR CODE GOES HERE ##
    first <- sample(1:n, size = 1)
    result.noswitch[i] <- doors[first]
    
    if (doors[first] == "car") {
      monty <- sample(1:n[-first], size=m)
    } else {
      monty <- sample(setdiff(1:n, c(first, which(doors == "car"))), size=m)
    }
  
    remain <- setdiff(1:n, c(first, monty))
    
    result.switch[i] <- doors[sample(remain, 1)]
  }
    
  # return a data frame with the two results
  return(data.frame(no_switch_result = mean(result.noswitch == "car"),
                    switch_result = mean(result.switch == "car")
                    )
  )
}

## Check
part_b_sim(3, 7)
```


#### Grade: 100/100 well done