---
title: "HW_B4"
author: "Yuhang Zhu"
date: "2023-11-03"
output: github_document
---


1. Below is code for simulating a coin flip. Try to understand what it does by running it, and then running the command `coin_flip()` in the console 10 times.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coin <- c("H", "T")
event_probs_coin <- c(0.5, 0.5)

coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_coin,
    replace = TRUE
  )
}

# running `coin_flip()` 10 times
coin_flip_10 <- replicate(10, coin_flip())
coin_flip_10
```

Copy and past the output from running `coin_flip()` 10 times in the console here:
"H" "T" "T" "H" "T" "H" "T" "T" "T" "T"

2. Write a function `X_coin()` that takes the result of `coin_flip()` as an argument (a string, "H" or "T"), and returns it into a 1 for "H" and 0 for "T". I've already started the code for you.
```{r}
set.seed(36850)
flip1 <- coin_flip()
flip2 <- coin_flip()
flip3 <- coin_flip()
flip4 <- coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.
X_coin <- function(flip){
  # fill in the code here
  # ifelse() is probably helpful
  ifelse(flip == "H", 1, 0)
}

# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_coin(flip1)
X_coin(flip2)
X_coin(flip3)
X_coin(flip4)
```

Treating `X_coin()` like a random variable describe it:

  a. What is the probability of 1?
  
  The `X_coin()` function operates as a Bernoulli trial, meaning it should adhere to the Bernoulli distribution. Therefore, the probability of 1 is 0.5, since the formula for this distribution is $f_X(x) = p^x(1-p)^{1-x} = p$ if $x=1$, and in this case, $p$ is equal to 0.5.
  
  b. What is the probability of 0?
  
  Based on the formula $f_X(x) = p^x(1-p)^{1-x} = 1-p$ when $x = 0$, the probability of 0 is 0.5
  
  c. What is the expectation of `X_coin()`?
  
  According to the formula $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p$, the expectation of `X_coin()` is 0.5.
  
  d. What is the variance of `X_coin()`?
  
  According to the formula $Var[X] = \sum_{i=0}^{1}(x_i - E[X])^2f_X(x) = (0-p)^2(1-p) + (1-p)^2p = p(1-p)$, the variance of `X_coin()` is 0.25.

3. Define a new function `biased_coin_flip()` that acts like `coin_flip()` except it returns "H" 70 percent of the time.
```{r}
set.seed(36850)

sample_space_coin <- c("H", "T")
event_probs_biased_coin <- c(0.7, 0.3)

biased_coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_biased_coin,
    replace = TRUE
  )
}
```

4. Define a new random variable `X_biased_coin()` that returns a 1 if flip is "H" and returns 0 if flip is "T"
```{r}
set.seed(36850)
flip1 <- biased_coin_flip()
flip2 <- biased_coin_flip()
flip3 <- biased_coin_flip()
flip4 <- biased_coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 
flip2 
flip3 
flip4 

X_biased_coin <- function(flip){
  # fill in the code here
  ifelse(flip == "H", 1, 0) # ifelse is helpful
}

# Use this to test out your code.
X_biased_coin(flip1)
X_biased_coin(flip2)
X_biased_coin(flip3)
X_biased_coin(flip4)
```

Treating `X_biased_coin()` like a random variable describe it:
  a. What is the probability of 1?
  
  The probability of 1 is 0.7.
  
  b. What is the probability of 0?
 
  The probability of 1 is 0.3.  

5. Using math, calculate:
  a. The expectation of `X_coin()`
  
  The expectation of `X_coin()` is $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p = 0.5$. 
  
  b. The expectation of `X_biased_coin()`
  
  The expectation of `X_biased_coin()` is $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p = 0.7$. 
  
  c. The expectation of `X_coin()` + `X_biased_coin()`
  
  Because `X_coin()` and `X_biased_coin()` are independent, the expectation of `X_coin()` + `X_biased_coin()` is $0.5 + 0.7 = 1.2$.

6. Use simulation to estimate:
  a. The expectation of `X_coin()`
  b. The expectation of `X_biased_coin()`
  c. The expectation of `X_coin()` + `X_biased_coin()`
  
I've filled in some code for your below
```{r}
set.seed(36850)

nsims <- 100000

# vectors where you can store the results of simulation for a, b, and c
X_coin_sims <- vector(mode = 'numeric', length = nsims)
X_biased_coin_sims <- vector(mode = 'numeric', length = nsims)
unbiased_plus_biased_coin_sims <- vector(mode = 'numeric', length = nsims)

# Code for part a: simulate X_coin
for(i in 1:nsims){
  sim_flip_i <- coin_flip()
  X_coin_sims[i] <- X_coin(sim_flip_i)
  
  sim__biasedflip_i <- #INSERT CODE#
  X_biased_coin_sims[i] <- #INSERT CODE#
  
  unbiased_plus_biased_coin_sims[i] <- #INSERT CODE#
  
}

# use head to see the first part of the result of the simulations
head(X_coin_sims)

# calculate the expectation of the simulations using mean()
mean(X_coin_sims)

# Now do the same thing for parts b and c

## INSERT CODE HERE ###

```

Compare your simulated results to the result you got via math in question 5. They should be very similar. If they're not, try to figure out why and fix it.


