---
title: "HW_B4"
author: "Yuhang Zhu"
date: "2023-11-03"
output: github_document
---

1. Below is code for simulating a coin flip. Try to understand what it does by running it, and then running the command `coin_flip()` in the console 10 times.
```{r}
set.seed(36850) # set random seed so that you get the same output everytime even though it's "random"

sample_space_coin <- c("H", "T")
event_probs_coin <- c(0.5, 0.5)

coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_coin,
    replace = TRUE
  )
}

# running `coin_flip()` 10 times
coin_flip_10 <- replicate(10, coin_flip())
coin_flip_10
```

Copy and past the output from running `coin_flip()` 10 times in the console here:
"H" "T" "T" "H" "T" "H" "T" "T" "T" "T"

2. Write a function `X_coin()` that takes the result of `coin_flip()` as an argument (a string, "H" or "T"), and returns it into a 1 for "H" and 0 for "T". I've already started the code for you.
```{r}
set.seed(36850)
flip1 <- coin_flip()
flip2 <- coin_flip()
flip3 <- coin_flip()
flip4 <- coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 # H
flip2 # T
flip3 # T
flip4 # H

# Function that acts like a random variable.
# returns 1 if flip == "H" and 0 otherwise.
X_coin <- function(flip){
  # fill in the code here
  # ifelse() is probably helpful
  ifelse(flip == "H", 1, 0)
}

# The code below should return a 1 for flip1 and flip4 and 0 for flip2 and flip3
X_coin(flip1)
X_coin(flip2)
X_coin(flip3)
X_coin(flip4)
```

Treating `X_coin()` like a random variable describe it:

  a. What is the probability of 1?
  
  The `X_coin()` function operates as a Bernoulli trial, meaning it should adhere to the Bernoulli distribution. Therefore, the probability of 1 is 0.5, since the formula for this distribution is $f_X(x) = p^x(1-p)^{1-x} = p$ if $x=1$, and in this case, $p$ is equal to 0.5.
  
  b. What is the probability of 0?
  
  Based on the formula $f_X(x) = p^x(1-p)^{1-x} = 1-p$ when $x = 0$, the probability of 0 is 0.5
  
  c. What is the expectation of `X_coin()`?
  
  According to the formula $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p$, the expectation of `X_coin()` is 0.5.
  
  d. What is the variance of `X_coin()`?
  
  According to the formula $Var[X] = \sum_{i=0}^{1}(x_i - E[X])^2f_X(x) = (0-p)^2(1-p) + (1-p)^2p = p(1-p)$, the variance of `X_coin()` is 0.25.

4. Define a new function `biased_coin_flip()` that acts like `coin_flip()` except it returns "H" 70 percent of the time.
```{r}
set.seed(36850)

sample_space_coin <- c("H", "T")
event_probs_biased_coin <- c(0.7, 0.3)

biased_coin_flip <- function(){
  sample(
    size = 1,
    x = sample_space_coin,
    prob = event_probs_biased_coin,
    replace = TRUE
  )
}
```

5. Define a new random variable `X_biased_coin()` that returns a 1 if flip is "H" and returns 0 if flip is "T"
```{r}
set.seed(36850)
flip1 <- biased_coin_flip()
flip2 <- biased_coin_flip()
flip3 <- biased_coin_flip()
flip4 <- biased_coin_flip()

# Example flips, they will always be the same because I set a random seed.
flip1 
flip2 
flip3 
flip4 

X_biased_coin <- function(flip){
  # fill in the code here
  ifelse(flip == "H", 1, 0) # ifelse is helpful
}

# Use this to test out your code.
X_biased_coin(flip1)
X_biased_coin(flip2)
X_biased_coin(flip3)
X_biased_coin(flip4)
```

Treating `X_biased_coin()` like a random variable describe it:
  a. What is the probability of 1?
  
  The probability of 1 is 0.7.
  
  b. What is the probability of 0?
 
  The probability of 1 is 0.3.  

5. Using math, calculate:
  a. The expectation of `X_coin()`
  
  The expectation of `X_coin()` is $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p = 0.5$. 
  
  b. The expectation of `X_biased_coin()`
  
  The expectation of `X_biased_coin()` is $E[X] = \sum_{i=0}^{1}x_if_X(x) = 0 + p = p = 0.7$. 
  
  c. The expectation of `X_coin()` + `X_biased_coin()`
  
  Because `X_coin()` and `X_biased_coin()` are independent, the expectation of `X_coin()` + `X_biased_coin()` is $0.5 + 0.7 = 1.2$.

6. Use simulation to estimate:
  a. The expectation of `X_coin()`
  b. The expectation of `X_biased_coin()`
  c. The expectation of `X_coin()` + `X_biased_coin()`
  
I've filled in some code for your below
```{r}
set.seed(36850)

nsims <- 100000

# vectors where you can store the results of simulation for a, b, and c
X_coin_sims <- vector(mode = 'numeric', length = nsims)
X_biased_coin_sims <- vector(mode = 'numeric', length = nsims)
unbiased_plus_biased_coin_sims <- vector(mode = 'numeric', length = nsims)

# Code for part a: simulate X_coin
for(i in 1:nsims){
  sim_flip_i <- coin_flip()
  X_coin_sims[i] <- X_coin(sim_flip_i)
  
  sim__biasedflip_i <- biased_coin_flip() #INSERT CODE#
  X_biased_coin_sims[i] <- X_biased_coin(sim__biasedflip_i) #INSERT CODE#
  
  unbiased_plus_biased_coin_sims[i] <- X_coin(sim_flip_i) + X_biased_coin(sim__biasedflip_i) #INSERT CODE#
}

# use head to see the first part of the result of the simulations
head(X_coin_sims)

# calculate the expectation of the simulations using mean()
mean(X_coin_sims)

# Now do the same thing for parts b and c

## INSERT CODE HERE ###
head(X_biased_coin_sims)

mean(X_biased_coin_sims)

head(unbiased_plus_biased_coin_sims)

mean(unbiased_plus_biased_coin_sims)
```

Compare your simulated results to the result you got via math in question 5. They should be very similar. If they're not, try to figure out why and fix it.

7. Imagine an experiment similar to the one we discussed. Students can use a drug, Getana. We are interested in studying the effect of Getana on student's GPA. In the code below, I've defined:
  a. A student index 1-6, it just assigns each student a number.
  b. A potential outcome for each student under treatment, Y1, and control, Y0. Note that the potential outcomes are the same, indicating that there is 0 effect
  
```{r}
student_index <- 1:6
Y1 <- c(4, 4, 3, 2, 1, 1)
Y0 <- Y1
```

Now, simulate what happens if we randomly sample 1 student to be in the Treatment group (so we see their GPA under Y1), and we sample a different student to be in Control (so we see their GPA under Y0). What will the average difference in GPA's be between the Treatment subject and Control subject? Compare the results to what you get if you simply subtract the mean of Y0 from the mean of Y1.

```{r}
set.seed(36850)

nsims <- 100000

gpa_treat_minus_control_sims <- vector(mode = "numeric",
                                       length = nsims)

for(i in 1:nsims){
  treated_subj_index <- sample(student_index, 
                               size = 1)
  control_subj_index <- sample(student_index[-treated_subj_index], 
                               size = 1)
  observed_treatement_GPA <- Y1[treated_subj_index] # fill in code, use treated_subj_index and Y1
  observed_control_GPA <- Y0[control_subj_index] # fill in code, use control_subj_index and Y0
    
  gpa_treat_minus_control_sims[i] <- observed_treatement_GPA - observed_control_GPA # What is the observed difference in gpas between treatment and control subjects?
}

# Calculate the average of gpa_treat_minus_control_sims
mean(gpa_treat_minus_control_sims)
mean(Y1 - Y0)
```

The simulation results indicate that with an increasing number of simulations, the difference in average GPA between the treatment and control groups converges 0.0145, closely approximating the true effect of $Y_1 - Y_0 = 0$.

7. Create a histogram of `gpa_treat_minus_control_sims` using ggplot. Make it look as good as you can, with proper axis labels.

```{r}
library(ggplot2)

gpa_diff <- as.data.frame(gpa_treat_minus_control_sims)
head(gpa_diff)

ggplot(gpa_diff, aes(gpa_treat_minus_control_sims)) + 
  geom_histogram(binwidth = 0.5) +
  scale_x_continuous(breaks = seq(-3, 3, by = 1)) + 
  scale_y_continuous(breaks = seq(0, 20000, by = 2500)) + 
  labs(x = "The Average Difference in GPA between the Treatment Subject and Control Subject",
       y = "Frequency") +
  theme(axis.title.x = element_text(vjust = -1),
        axis.title.y = element_text(vjust = 2))
```

8. Repeat questions 7 and 7 above for the new potential outcomes defined below. Compare the results to what you get if you simply subtract the mean of Y0 from the mean of Y1.

```{r}
set.seed(36850)
student_index <- 1:6
Y1 <- c(4, 4, 3, 3, 4, 1)
Y0 <- c(2, 1, 4, 2, 1, 1)
```

```{r}
set.seed(36850)

nsims <- 100000

gpa_treat_minus_control_sims <- vector(mode = "numeric",
                                       length = nsims)

for(i in 1:nsims){
  treated_subj_index <- sample(student_index, 
                               size = 1)
  control_subj_index <- sample(student_index[-treated_subj_index], 
                               size = 1)
  observed_treatement_GPA <- Y1[treated_subj_index] # fill in code, use treated_subj_index and Y1
  observed_control_GPA <- Y0[control_subj_index] # fill in code, use control_subj_index and Y0
    
  gpa_treat_minus_control_sims[i] <- observed_treatement_GPA - observed_control_GPA # What is the observed difference in gpas between treatment and control subjects?
}

# Calculate the average of gpa_treat_minus_control_sims
mean(gpa_treat_minus_control_sims)
mean(Y1 - Y0)
```

The simulation results indicate that with an increasing number of simulations, the difference in average GPA between the treatment and control groups converges 1.335, closely approximating the true effect of $Y_1 - Y_0 = 1.333$.