---
title: "Excercises from 4.4 of R 4 Data Science"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
  html_notebook:
    keep-md: yes
---

# A1 Homework 4.4 R4DS exercises

## 1. Why Does this code not work.

The following code

``` r
my_variable <- 10 
my_varıable 
```

Throws an error because the variable referenced in the second line `my_varıable` is not the same as the variable `my_variable`. The i is a different symbol. If we were to change the code to the code below, it will run correctly and return 10.

```{r}
my_variable <- 10 
my_variable 
```

## 2. Tweak each of the following R commands so that they run correctly

To fix the code below, you need to fix a number of typos

``` r
library(tidyverse)

ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

I've noted the correction as a comment on each line

```{r}
library(tidyverse)

ggplot(data = mpg) + # change dota to data
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8) # change fliter to filter and = to ==
                      # = is used for assignment, but we want == to filter based on the logical condition:
                      # "does cyl equal 8?"
filter(diamonds, carat > 3) # changed diamond to diamonds. diamonds is a dataset that comes with R. diamond is not.
```

## Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

A shortcut menu pops up. You can find the same command by going to the `Tools` menu in RStudio
